### 2024-01-14 Paper/main.tex
Change images to pgfs in Paper
Feature/unify plots (#87)
* Add time measure to quality evaluation

* change plots to pgf

* add pgf plots and np results file for quality

* remove comments

* change accuracy plot and save fig as .pgf

* add pgf plorts from plot resutls py

* add pgf plots with pngs and npy results

* Normalize plots

* add pgf plots

* Change images to pgfs in Paper

---------

Co-authored-by: Michael Hafner <hafneer@gmail.com>
Co-authored-by: Stefan Findenig <s.findenig@gmail.com>
Co-authored-by: aleksandarRa <radovic.aleksandar@gmx.at>
Add description for no transfer learnin

\begin{figure}[h!]
	\centering
	\includegraphics[width=12cm]{filesize_comparison.png}
	\caption{Archived filesizes for used encoder}
	\label{fig: fsize_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{psnr.png}
          \caption{PSNR comparison of the used codecs}
          \label{fig: psnr_comparison}
      \end{subfigure}
      \hfill
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../Plots/ssim.png}
          \caption{SSIM comparison of the used codecs}
          \label{fig:CI}
      \end{subfigure}
\caption{
\label{fig: comparison}%
Comparison of PSNR and SSIM}
\end{figure}

@@

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=12cm]{accuracy_comparison.png}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.7\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{loss_comparison_filesize_10.png}
        \caption{Loss of model with filesize 10}
        \label{fig:loss_comparison_filesize_10}
    \end{minipage}\hfill
    \begin{minipage}{0.7\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{loss_comparison_mixed.png}
        \caption{Loss of mixed model}
        \label{fig:loss_comparison_filesize_mixed}
    \end{minipage}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/filesize_to_target.pgf}}
	\caption{Archived filesizes for used encoder}
	\label{fig: fsize_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
      \begin{subfigure}{0.49\textwidth}
        \resizebox{\textwidth}{!}{\input{../Plots/psnr.pgf}}
          \caption{PSNR comparison of the used codecs}
          \label{fig: psnr_comparison}
      \end{subfigure}
      \hfill
      \begin{subfigure}{0.49\textwidth}
        \resizebox{\textwidth}{!}{\input{../Plots/ssim.pgf}}
          \caption{SSIM comparison of the used codecs}
          \label{fig:CI}
      \end{subfigure}
\caption{
\label{fig: comparison}%
Comparison of PSNR and SSIM}
\end{figure}

@@

\subsection{Evaluation of ResNet Performance Without Transfer Learning} 
Prior to the implementation of transfer learning methodologies, an analysis was conducted to ascertain whether the selected ResNet architecture could independently identify various image compression algorithms. The entire dataset of one specific compression size, was processed through the model, and the outputs were L2 normalized. This resulted in 1000 dimension vectors for each image.

To make sense of these results, we used Principal Component Analysis (PCA) on all the vectors and plotted them on a scatter plot as it can be seen in Figure \ref{fig: no_transfer}. The scatter plot reveals that for images compressed to 10kB, there is no discernible clustering pattern specific to a single compression algorithm. However, it is observed that certain clusters exist where multiple compression algorithms are in close proximity to each other. This observation aligns with the inherent capability of the original network to classify images. Consequently, the images utilized across different compression algorithms form these compact clusters.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{Plots/plot_scatter_without_transfer_10.pgf}
	\caption{10kB Compression: ResNet without transfer learning}
	\label{fig: no_transfer}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison.pgf}}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.7\textwidth}
        \centering
        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_10_model.pgf}}
        \caption{Loss of model with filesize 10}
        \label{fig:loss_comparison_filesize_10}
    \end{minipage}\hfill
    \begin{minipage}{0.7\textwidth}
        \centering
        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_mixed_model.pgf}}
        \caption{Loss of mixed model}
        \label{fig:loss_comparison_filesize_mixed}
    \end{minipage}
\end{figure}
